### 2024-06-27 basic-statistics.qmd
20240627 - legend location

ggplot2::ggplot(
  data = observedGroups,
  mapping = aes(
    x = score,
    fill = group,
    color = group
  )
) +
  geom_density(alpha = 0.5) +
  scale_color_manual(values = c("red", "blue")) +
  scale_fill_manual(values = c("red","blue")) +
  geom_vline(xintercept = mean(observedGroups$score[which(observedGroups$group == "Group 1")])) +
  geom_vline(xintercept = mean(observedGroups$score[which(observedGroups$group == "Group 2")])) +
  ggplot2::labs(
    x = "Score",
    y = "Frequency",
    title = "What is the probability my data would look like this..."
  ) +
  ggplot2::theme_classic(
    base_size = 16) +
  ggplot2::theme(
    legend.title = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank())

ggplot2::ggplot(
  data = populationGroups,
  mapping = aes(
    x = score,
    fill = group,
    color = group
  )
) +
  geom_density(alpha = 0.5) +
  scale_color_manual(values = c("red", "blue")) +
  scale_fill_manual(values = c("red","blue")) +
  geom_vline(xintercept = mean(populationGroups$score[which(populationGroups$group == "Group 1")])) +
  geom_vline(xintercept = mean(populationGroups$score[which(populationGroups$group == "Group 2")])) +
  ggplot2::labs(
    x = "Score",
    y = "Frequency",
    title = "...if in the population, the groups were really this:"
  ) +
  ggplot2::theme_classic(
    base_size = 16) +
  ggplot2::theme(
    legend.title = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank())
```

>>>>

ggplot2::ggplot(
  data = observedGroups,
  mapping = aes(
    x = score,
    fill = group,
    color = group
  )
) +
  geom_density(alpha = 0.5) +
  scale_color_manual(values = c("red", "blue")) +
  scale_fill_manual(values = c("red","blue")) +
  geom_vline(xintercept = mean(observedGroups$score[which(observedGroups$group == "Group 1")])) +
  geom_vline(xintercept = mean(observedGroups$score[which(observedGroups$group == "Group 2")])) +
  ggplot2::labs(
    x = "Score",
    y = "Frequency",
    title = "What is the probability my data would look like this..."
  ) +
  ggplot2::theme_classic(
    base_size = 16) +
  ggplot2::theme(
    legend.title = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    #plot.title.position = "plot"
    legend.position = "inside",
    legend.margin = margin(0, 0, 0, 0),
    legend.justification.top = "left",
    legend.justification.left = "top",
    legend.justification.bottom = "right",
    legend.justification.inside = c(1, 1),
    legend.location = "plot")

ggplot2::ggplot(
  data = populationGroups,
  mapping = aes(
    x = score,
    fill = group,
    color = group
  )
) +
  geom_density(alpha = 0.5) +
  scale_color_manual(values = c("red", "blue")) +
  scale_fill_manual(values = c("red","blue")) +
  geom_vline(xintercept = mean(populationGroups$score[which(populationGroups$group == "Group 1")])) +
  geom_vline(xintercept = mean(populationGroups$score[which(populationGroups$group == "Group 2")])) +
  ggplot2::labs(
    x = "Score",
    y = "Frequency",
    title = "...if in the population, the groups were really this:"
  ) +
  ggplot2::theme_classic(
    base_size = 16) +
  ggplot2::theme(
    legend.title = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    #plot.title.position = "plot",
    legend.position = "inside",
    legend.margin = margin(0, 0, 0, 0),
    legend.justification.top = "left",
    legend.justification.left = "top",
    legend.justification.bottom = "right",
    legend.justification.inside = c(1, 1),
    legend.location = "plot")
```
